Invariant Representations for Noisy Speech Recognition

### 2016-12-01 poster.tex
Fix articles, emphasize definitions and important results

\begin{document}
\addtobeamertemplate{headline}{} 
{
\begin{tikzpicture}[remember picture,overlay] 
\node [shift={(-13 cm,-7cm)}] at (current page.north east)
% \node [shift={(-10 cm,-5cm)}] at (current page.north west)
{\includegraphics[height=7cm]{ibmpos_blue}}; 
%\node [shift={(-42 cm,-11cm)}] at (current page.north)
%{\includegraphics[height=7cm]{UdeM_CMJK.eps}}; 
\node [shift={(-49 cm,-6cm)}] at (current page.north)
% \node [shift={(-10 cm,-5cm)}] at (current page.north west)
{\includegraphics[height=9cm]{MILA_2C.eps}}; 
\end{tikzpicture} 
}

@@

\begin{block}{Generative Adversarial Networks}
    \begin{itemize}
        \item Two networks: the generator and the discriminator.
        \item The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a sample, e.g. an image, 
    similar to the images in the training set.

@@

\begin{block}{Domain Adaptation with Reverse Gradient}
    \begin{itemize}
        \item \cite{ganin2014unsupervised} proposes $Y$-shaped network: the image is fed to the
        encoder network ($E$) which produces a hidden representation $h$.

@@

        \item The goal of training is to learn the hidden 
        representation that is invariant to the domain labels and performs well on the target classification 
        task.

@@

        \begin{column}{\onecolwid} % The second column
            \begin{block}{{\Large Invariant Representation Network}}
                \begin{itemize}
                    \item The model consists of three neural networks. 
                    \item The encoder $E$ produces
                        the intermediate representation $h$ which used in the recognizer $R$ and 
                        in the domain discriminator $D$. 
                    \item The hidden representation $h$ is trained to improve
                        the recognition and minimize the domain discriminator performance. 
                    \item The domain discriminator
                        is a classifier trained to maximize its accuracy on the noise type
                        classification task.
                \end{itemize}
                \begin{equation*}
                    L = L_1(\hat{y}, y; \theta_R, \theta_E) + 
                    \alpha L_2(\hat{d}, d; \theta_D) -
                    \beta L_3(\hat{d}, d; \theta_E)
                \end{equation*}

                \begin{figure}
                    \centering
                    \includegraphics[width=0.9\linewidth]{model.pdf}
                \end{figure}

                \begin{itemize}
                    \item The model is a DNN-HMM system with a feed-forward neural network trained to predict the 
                        CD HMM state (2000 classes).
                    \item Input: 40-dimensional Mel-filterbank features with their deltas and 
                        delta-deltas spliced over $\pm$5 frames (total dimension is 1320).
                    \item Baseline: 6-layer DNN with 2048 rectified linear units at every layer.
                    \item The right branch that predicts the domain (noise condition). This branch is discarded 
                        in the testing phase. 
                    \item The noise condition is the domain label. We are merging all noise types into one label
                        and clean as the other label.
                    \item The invariance term is
                        \begin{equation*}
                            L_3 = d\log(1 - \hat{d}) + (1-d)\log(\hat{d}),
                        \end{equation*}
                        where $d$ is the domain label and $\hat{d}$ is the network prediction.
                \end{itemize}
            \end{block}

@@

                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. 
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
                Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}

@@

    Average word error rate (WER\%) on Aurora-4 dataset on all test conditions,
        including seen and unseen noise and unseen microphone. First column
        is the number of noise conditions used for the training. The last row is a 
        preliminary experiment with layer-wise pre-training close to state-of-the-art
        model and a corresponding invariance training starting with a pretrained model.
\begin{table}
    \centering
    \label{tab:results}
    \begin{tabular}{r|cc||cc|cc|cc|cc}
        Noise       &Inv&BL&  \multicolumn{2}{c|}{A} & \multicolumn{2}{c|}{B} & \multicolumn{2}{c|}{C} & \multicolumn{2}{c}{D}\\
        cond  & & &  Inv & BL & Inv & BL & Inv & BL & Inv & BL\\
    \hline
    1           &16.36        &18.14 &6.54&7.57    &12.71& 14.09   & 11.45&   13.10    & 22.47 &   24.80    \\
    2           &15.56        &17.39 &5.90&  6.58 &   11.69   &13.28   &11.12   &13.51   &21.79   &23.96 \\
    3           &14.24        &14.67 &5.45 & 5.08&    10.76&   12.44&   9.75&    9.84 &   19.93&   19.30\\
    4           &13.61        &13.84 & 5.08 &5.29    &9.73    &9.97    &9.49    &9.56    &19.49   &19.90\\         
    5           &13.41        &13.02 & 5.12 &5.34    &9.52    &9.42    &9.55    &8.67    &19.33   &18.65\\         
    6           &12.62        &12.60 & 4.80 &4.61    &9.04    &8.86    &8.76    &8.59    &18.16   &18.21\\
    \hline\hline
    6*          &11.85        &11.99 &4.52    &4.76    &8.76    &8.76    &7.79    &8.57    &16.84&    16.99
    \end{tabular}
\end{table}
\end{block}

>>>>

\begin{document}
\addtobeamertemplate{headline}{} 
{
\begin{tikzpicture}[remember picture,overlay] 
\node [shift={(-13 cm,-6cm)}] at (current page.north east)
% \node [shift={(-10 cm,-5cm)}] at (current page.north west)
{\includegraphics[height=7cm]{ibmpos_blue}}; 
%\node [shift={(-42 cm,-11cm)}] at (current page.north)
%{\includegraphics[height=7cm]{UdeM_CMJK.eps}}; 
\node [shift={(-49 cm,-6cm)}] at (current page.north)
% \node [shift={(-10 cm,-5cm)}] at (current page.north west)
{\includegraphics[height=9cm]{MILA_2C.eps}}; 
\end{tikzpicture} 
}

@@

\begin{block}{Generative Adversarial Networks}
    \begin{itemize}
        \item Two networks: the \textcolor{dblue}{generator} and the \textcolor{dblue}{discriminator}.
        \item The generator network $G$ has an
    input of randomly-generated feature vectors and is asked to produce a sample, e.g. an image, 
    similar to the images in the training set.

@@

\begin{block}{Domain Adaptation with Reverse Gradient}
    \begin{itemize}
        \item \cite{ganin2014unsupervised} proposes a $Y$-shaped network: the image is fed to the
        encoder network ($E$) which produces a hidden representation $h$.

@@

        \item The goal of training is to learn a hidden 
        representation that is invariant to the domain labels and performs well on the target classification 
        task.

@@

        \begin{column}{\onecolwid} % The second column
            \begin{block}{{\Large Invariant Representation Network}}
                \begin{itemize}
                    \item Our model consists of three neural networks. 
                    \item The \textcolor{dblue}{encoder} $E$ produces
                        the intermediate representation $h$ which used in the \textcolor{dblue}{recognizer} $R$ and 
                        in the \textcolor{dblue}{domain discriminator} $D$. 
                    \item The hidden representation $h$ is trained to improve
                        the recognition and minimize the domain discriminator performance. 
                    \item The domain discriminator
                        is a classifier trained to maximize its accuracy on the noise type
                        classification task.
                \end{itemize}
                \begin{equation*}
                    L = L_1(\hat{y}, y; \theta_R, \theta_E) + 
                    \alpha L_2(\hat{d}, d; \theta_D) -
                    \beta L_3(\hat{d}, d; \theta_E)
                \end{equation*}

                \vspace{2cm}
                \begin{figure}
                    \centering
                    \includegraphics[width=0.7\linewidth]{model.pdf}
                \end{figure}
                \vspace{2cm}

                \begin{itemize}
                    \item The model is a DNN-HMM system with a feed-forward neural network trained to predict the 
                        CD HMM state (2000 classes).
                    \item Input: 40-dimensional mel-filterbank features with their deltas and 
                        delta-deltas spliced over $\pm$5 frames (total dimension is 1320).
                    \item Baseline: 6-layer DNN with 2048 rectified linear units at every layer.
                    \item The right branch that predicts the domain (noise condition). This branch is discarded 
                        in the testing phase. 
                    \item The noise condition is the domain label. We are merging all noise types into one label
                        and clean as the other label.
                    \item The invariance term is
                        \begin{equation*}
                            L_3 = d\log(1 - \hat{d}) + (1-d)\log(\hat{d}),
                        \end{equation*}
                        where $d$ is the domain label and $\hat{d}$ is the network prediction.
                \end{itemize}
            \end{block}

@@

                \vspace{1cm}
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_avg.pdf}
                \end{figure}
                Average performance of the baseline multi-condition and invariance model varying with the 
                number of noise conditions used for training. 
                \vspace{4cm}
                \begin{figure}
                    \centering
                    \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
                \end{figure}
                Average performance on seen versus 
                unseen noise conditions.
                Testing was performed on all wv1 conditions (Sennheiser microphone).
            \end{block}
        \end{column} % end of third column
    \end{columns}
\end{column}

@@

    Average word error rate (WER\%) on Aurora-4 dataset on all test conditions,
        including seen and unseen noise and unseen microphone. First column
        is the number of noise conditions used for the training. The last row is a 
        preliminary experiment with layer-wise pre-training close to state-of-the-art
        model and a corresponding invariance training starting with a pretrained model.
\begin{table}
    \centering
    \label{tab:results}
    \begin{tabular}{r|rr||rr|rr|rr|rr}
        Noise       &&&  \multicolumn{2}{c|}{A} & \multicolumn{2}{c|}{B} & \multicolumn{2}{c|}{C} & \multicolumn{2}{c}{D}\\
        cond  & Inv & BL &  Inv & BL & Inv & BL & Inv & BL & Inv & BL\\
    \hline
    1           &\textcolor{dblue}{16.36}        &18.14 & 6.54  & 7.57    &12.71& 14.09   & 11.45&   13.10    & 22.47 &   24.80    \\
        2           &\textcolor{dblue}{15.56}        &17.39 & 5.90  & 6.58    &   11.69   &13.28   &11.12   &13.51   &21.79   &23.96 \\
        3           &\textcolor{dblue}{14.24}        &14.67 & 5.45  & 5.08    &   10.76&   12.44&   9.75&    9.84 &   19.93&   19.30\\
        4           &\textcolor{dblue}{13.61}        &13.84 & 5.08  & 5.29    &9.73    &9.97    &9.49    &9.56    &19.49   &19.90\\         
        5           &13.41        &\textcolor{dblue}{13.02} & 5.12  & 5.34    &9.52    &9.42    &9.55    &8.67    &19.33   &18.65\\         
        6           &12.62        &\textcolor{dblue}{12.60} & 4.80  & 4.61    &9.04    &8.86    &8.76    &8.59    &18.16   &18.21\\
    \hline\hline
    6*          &\textcolor{dblue}{11.85}        &11.99 &4.52    &4.76    &8.76    &8.76    &7.79    &8.57    &16.84&    16.99
    \end{tabular}
\end{table}
\end{block}
